    \documentclass[12pt]{deedy-resume-openfont}

    \begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Profile
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Ivan}{Lin}{ivlin112@gmail.com | (917) 680 - 2208 | github.com/ivlin | ivlin.github.io}{1675 68th St, Brooklyn NY 11204}
\sectionsep

\fontfamily{lmss}\selectfont
\raggedright

April 21st, 2019\\
\sectionsep


Birchbox\\
New York, New York\\
\sectionsep

Dear Birchbox,\\
\sectionsep

I am an undergraduate computer science and applied mathematics student from Stony Brook University applying for your Software Engineering Internship. As a student and developer, I have been involved in computer science through a number of academic, personal, and professional projects that have given me the ability to apply my knowledge to real world systems.\\
\sectionsep

In school, I’ve taken classes such as Operating Systems, Machine Learning, Computer Networks, and Computer Security. Outside of the classroom, I’ve worked on both personal and professional software projects. In my most recent internship as a full stack software developer at Sweetist, I wrote unit tests, modified the design of the company’s website, and implemented a number of new features such as graphs for displaying shipping data. In my time there, I had to quickly familiarize myself with Ruby on Rails, Postgres, and the Heroku deployment process. I was also able to apply and improve my skills with HTML, CSS, and Javascript. I have since used these tools alongside other skills in my own personal projects, which includes my website, an interactive statistics visualization program, and an in-terminal text editor for quickly renaming files. But above any language or library, I know how to work in a team, including the necessity for clear code documentation, verbal communication, and proper git management. At my previous internship, I not only had detailed commits and branches, but also worked with CircleCI. Through my experiences, I’ve worked both alone and in teams with technologies that ranged from low level systems to high level frameworks.\\
\sectionsep

I know I am still learning and have much to gain from participating in this internship. You are looking for someone with some skills to offer, but can also quickly learn new technologies. I have proven that I can do just that.\\
\sectionsep

Thank you for your time and consideration. I look forward to hearing your response.\\
\sectionsep

Best regards,\\
Ivan Lin
\end{document}
